cooking

### 2019-10-02 inst/cook.Rmd
more work: clearer implications

Note that noone is allowed to vote for themselves.  We may find
maximum likelihood estimate for the strengths,
$\operatorname{argmax}\mathcal{L}\left(p_1,\ldots,p_5\right)$
Graphically:

@@

(observe that the hypothesis with the maximum likelihood is
$p_2\geqslant p_1$).  Compare with the unconstrained maximum:

@@

short of Edwards's two-units-of-support criterion.

>>>>

Note that noone is allowed to vote for themselves.  We may find
maximum likelihood estimate for the strengths,
$\operatorname{argmax}\mathcal{L}\left(p_1,\ldots,p_5\right)$:

```{r}
maxp(H)
```

Graphically:

@@

Observe that the hypothesis with the maximum likelihood is
$p_2\geqslant p_1$, as might be expected on the grounds that in the
unconstrained case we have
$\hat{p_2}>\max\left(\hat{p_3},\hat{p_4},\hat{p_5}\right)$.  Now
compare the constrained maximum with the unconstrained maximum:

@@

short of Edwards's two-units-of-support criterion.  There is no strong
evidence to support the assertion that person 1 is actually stronger
than person 2 in the sense that $p_1>p_2$.
